---
title: "P8105 Homework 5"
author: Heidi Lumish
output: github_document
---

```{r setup, include=FALSE}
library(readr)
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

#### Import the data
First we will import the data from the GitHub repository.

```{r}
urlfile="https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicides <- read_csv(url(urlfile))
```

#### Description of the data

Create a city_state variable (e.g. "Baltimore, MD") and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r}
homicides_city = homicides %>% 
  mutate(
    city_state = paste(city, state, sep = ", "),
    unsolved = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", 1, 0)
    ) %>%
  group_by(city_state) %>%
  mutate(
    number_murders = n(),
    number_unsolved = sum(unsolved)) %>% 
  select(city_state, number_murders, number_unsolved) %>%   unique()
```

Run prop.test for Baltimore, MD

```{r}
homicides_city %>% 
  filter(city_state == "Baltimore, MD")

proportion = function (x, n) {
  
  prop = prop.test(x, n)
  
  return(prop)
}

prop_baltimore = prop.test(1825, 2827)
broom::tidy(prop_baltimore)
```


Run prop.test for each of the cities in the dataset and extract proportion of unsolved homicides and confidence interval.

```{r}
homicides_nested = homicides_city %>% 
  nest(data = number_murders:number_unsolved)

```

## Problem 2

#### Import and tidy the data

First we will import the data from the longitudinal study. Since data for each participant is included in a separate file, first we create a dataframe containing all file names (which are the subject ID and arm). Next we will write a function to read data from the csv files. Then we will use the purrr::map function to read in the data for each subject. Finally, we will tidy the data by unnesting it, separating the arm and subject IDs into separate columns, and using pivot longer to create a "week" variable.

```{r}
files_df = 
  tibble(file_name = list.files("./data")) 

subject_data = function(file_name){
  
  data = read_csv(str_c("./data/", file_name))
  
  return(data)
  
}

observations = files_df %>% 
  mutate(data = map(file_name, subject_data)) %>%
  unnest(data) %>%
  separate(file_name, c("arm", "subject_id"), "_") %>%
  mutate(subject_id = substr(subject_id, 1, 2),
         subject_id = as.numeric(subject_id)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>% 
  mutate(week = as.numeric(week))
```

#### Spaghetti plot

Next we will make a spaghetti plot showing observations on each subject over time. 

```{r}
observations %>% 
  ggplot(aes(x = week, y = observations, color = arm)) +
  geom_point(size = .2) + 
  geom_line(aes(group = interaction(arm, subject_id)), alpha = .3) +
  labs(
    title = "Observations among experimental and control groups \nover time",
    x = "Week",
    y = "Observed Values") +
  scale_color_discrete(name = "Arm", labels = c("Control", "Experimental"))
```

The spaghetti plot shows that the values among the control subjects are relatively constant over time, whereas the values for the experimental subjects increase over time.

Alternative to maps function above
```{r}
files_df %>% 
  mutate(data = subject_data(file_name)) %>% view()
```

## Problem 3

#### Load the iris dataset and introduce missing values

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function that replaces missing values

```{r}
missing = function(x){
  if (is.character(x)) {
    x[is.na(x)] <- "virginica"
  }
  
  if (!is.character(x)) {
  x[is.na(x)] <- mean(x, na.rm = TRUE)

  }
  
  return(x)
}

missing(iris_with_missing$Sepal.Length)

iris_with_missing %>%
  mutate(Sepal.Length = map(Sepal.Length, missing),
         Sepal.Width = map(Sepal.Width, missing),
         Petal.Length = map(Petal.Length, missing),
         Petal.Width = map(Petal.Width, missing),
         Species = map(Species, missing)) %>%  view()

```

