---
title: "P8105 Homework 5"
author: Heidi Lumish
output: github_document
---

```{r setup, include=FALSE}
library(readr)
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

#### Import the data
First we will import the data from the GitHub repository.

```{r}
urlfile="https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicides <- read_csv(url(urlfile))
```

#### Description of the data

Create a city_state variable (e.g. "Baltimore, MD") and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r}
homicides_city = homicides %>% 
  mutate(
    city_state = paste(city, state, sep = ", "),
    unsolved = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", 1, 0)
    ) %>%
  group_by(city_state) %>%
  mutate(
    number_murders = n(),
    number_unsolved = sum(unsolved)) %>% 
  select(city_state, number_murders, number_unsolved) %>%   unique()
```

Run prop.test for Baltimore, MD

```{r}
homicides_city %>% 
  filter(city_state == "Baltimore, MD")

proportion = function (x, n) {
  
  prop = prop.test(x, n)
  
  return(prop)
}

prop_baltimore = prop.test(1825, 2827)
broom::tidy(prop_baltimore)
```


Run prop.test for each of the cities in the dataset and extract proportion of unsolved homicides and confidence interval.

```{r}
homicides_nested = homicides_city %>% 
  nest(data = number_murders:number_unsolved)

```

## Problem 2

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

